---
title: "p8105_hw5_hm2946.Rmd"
author: "min"
date: "2022-11-13"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

*read the data*
```{r}
p1_data = 
  tibble(
    files = list.files("data/problem1/"),
    path = str_c("data/problem1/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest(cols = c(data))
```

*Clean the data*
```{r}
p1_tidy = 
  p1_data %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

*plot*
```{r}
p1_tidy %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

In the control arm: the outcome doesn't change much as time passes
In the experiment arm: the outcome increases linearly as time passes

## Problem 2

*read the data*
```{r}
homi_raw = read_csv("data/homicide-data.csv") 
```

There are 52179 observations in total, and each observation is identified with uid and reported date. Then it contains name, age and gender of the victims. It describes the city, state, latitude and longitude of the criminal scene. Finally it tells the results of the cases.

*Clean the data*
```{r}
homi_tidy1 = homi_raw %>% 
  mutate(city_state = str_c(city,state,sep = ","),
         unsolved = ifelse(disposition == c("Closed without arrest","Open/No arrest"),1,0)) %>% 
  select(city_state,unsolved) %>% 
  count(city_state) %>% 
  rename("total_cases" = n)

homi_tidy = homi_raw %>% 
  mutate(city_state = str_c(city,state,sep = ","),
         unsolved = ifelse(disposition == c("Closed without arrest","Open/No arrest"),1,0)) %>% 
  select(city_state,unsolved) %>% 
  count(city_state, wt = unsolved) %>% 
  rename("unsolved_cases" = n) %>% 
  left_join(homi_tidy1)
```

*Balt test*
```{r}
balt_test = homi_tidy %>% 
  filter(city_state == "Baltimore,MD") %>% 
  mutate(prop_test = map2(unsolved_cases,total_cases,~prop.test(.x,.y) %>%
  broom::tidy())) %>% 
  unnest(cols = c(prop_test))

balt_test %>% 
  select(city_state,estimate,conf.low,conf.high)
```

*Test all*
```{r}
all_test = homi_tidy %>% 
  mutate(prop_test = map2(unsolved_cases,total_cases,~prop.test(.x,.y) %>%
  broom::tidy())) %>% 
  unnest(cols = c(prop_test)) %>% 
  select(city_state,estimate,conf.low,conf.high)
```

*Plot*
```{r}
all_test %>%  
  mutate(
    city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Problem 3

```{r}
set.seed(1)
```

*simulation*
```{r}
t_test = function(mu){
  
  sample = rnorm(30, mu, 5)
  result = t.test(sample) %>% 
    broom::tidy()
  
  result
}

sim_results_df = 
  expand_grid(
    mu = c(0, 1, 2, 3, 4, 5, 6),
    iter = 1:50
  ) %>% 
  mutate(estimate_df = map(mu, t_test)) %>% 
  unnest(estimate_df) %>% 
  select(mu, "mu_hat" = estimate, p.value)

```

#### Plot 1
```{r}
sim_results_df %>% 
  select(mu, p.value) %>% 
  filter(p.value < 0.05) %>% 
  count(mu) %>% 
  mutate(null_rejected_proportion = n/50) %>% 
  ggplot(aes(x = mu, y = null_rejected_proportion)) + 
  geom_point() 
```

#### Plot 2
